Computational musicology, ????, Profit

### 2016-07-25 paper.tex
Fix quotes.
Don't hide anything in the abstract.

\begin{abstract}
In this paper I propose a novel method for converting computational musicology into profit. While my particular example
is tongue-in-cheek, it shows that algorithmic composition and analysis can help us deconstruct and disrupt
traditional notions of musical authorship. I adopt literary modes of analysis and presentation, which I motivate by
arguing that music is a cultural and artistic phenomenon rather than a natural one.
\end{abstract}

@@

Coutinho et al. resolve this ``puzzling old problem" a different way. They observe that while in biology ``fossils can be studied
to understand the
past and evolution of species", music lacks a corresponding natural object for them to base their research
upon\cite{Computational Musicology}. Their solution is to turn to modelling and simulation as a substitute that allows them
to make their work "scientifically sound".

>>>>

\begin{abstract}
In this paper I examine the relationship of complexity theory and disjunctive sequences to music, music-generating programs and
literary works. I then apply the theory to devising a program to generate an infinite `copyright infringement song' that contains
all other songs within it. I adopt literary modes of analysis and presentation, which I motivate by
arguing that music is a cultural and artistic phenomenon rather than a natural one.
\end{abstract}

@@

Coutinho et al. resolve this ``puzzling old problem" a different way. They observe that while in biology ``fossils can be studied
to understand the
past and evolution of species", music lacks a corresponding natural object for them to base their research
upon\cite{Computational Musicology}. Their solution is to turn to modelling and simulation as a substitute that allows them
to make their work ``scientifically sound".
